### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
sethi larger (0.3) noise

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`

@@

``` {r runall}
lvl <- 0.1
det <- scenario(0.01, 0.0, 0.0)
g   <- scenario(lvl, 0.0, 0.0)
m   <- scenario(0.0, lvl, 0.0)
i   <- scenario(0.0, 0.0, lvl)
gm  <- scenario(lvl, lvl, 0.0)
gi  <- scenario(lvl, 0.0, lvl)
im  <- scenario(0.0, lvl, lvl)
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r sethiplots, dependson="runall"}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("deterministic", "growth", "measure", "implement", "growth+measure", "growth+implement", "all")
print(xtable(matrix(means$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=7, dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters_bignoise/", verbose=TRUE or`

@@

Determine the policies for each of the scenarios (noise combinations).

``` {r runall}
lvl <- 0.3
````

``` {r }
det <- scenario(0.01, 0.0, 0.0)
````

``` {r }
g   <- scenario(lvl, 0.0, 0.0)
````

``` {r }
m   <- scenario(0.0, lvl, 0.0)
````

``` {r }
i   <- scenario(0.0, 0.0, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0.0)
````

``` {r }
gi  <- scenario(lvl, 0.0, lvl)
````

``` {r }
mi  <- scenario(0.0, lvl, lvl)
````

``` {r }
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r sethiplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], 
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), smi = c(0, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- c("det", "growth", "measure", "impl", "growth+measure", "growth+impl", "impl+measure" "all")
print(xtable(matrix(means$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=8, dimnames=list(uncertainties, uncertainties))), type="html")
````
